# Multilevel Visualization

> "Mathematical Science shows us what is. It is the language of unseen relations between things. But to use & apply that language we must be able fully to appreciate, to feel, to seize, the unseen, the unconscious. Imagination too shows us what is, the is that is beyond the senses." [@Lovelace]

## Introduction

Below, I describe the use of [Stata](https://www.stata.com/) [@StataCorp2021:3], [R](https://www.r-project.org/) [@RProgram], and [Julia](https://www.julialang.org/) [@JuliaArticle] to visualize multilevel models. 

## The Data {#sec-data}

The examples use the `simulated_multilevel_data.dta` file from [*Multilevel Thinking*](https://agrogan1.github.io/multilevel-thinking/simulated-multi-country-data.html). Here is a [direct link](https://github.com/agrogan1/multilevel-multilingual/raw/main/simulated_multilevel_data.dta) to download the data.

```{r}
#| echo: false
#| output: false

file.copy("../multilevel-thinking/simulate-and-analyze-multilevel-data/simulated_multilevel_data.dta", 
          ".",
          overwrite = TRUE) # copy over most recent version

file.copy("../multilevel-thinking/simulate-and-analyze-multilevel-data/simulated_multilevel_longitudinal_data.dta", 
          ".",
          overwrite = TRUE) # copy over most recent version

```

```{r}
#| echo: false
#| label: tbl-multilingual1
#| tbl-cap: Sample of Simulated Multilevel Data

library(haven) # read Stata

library(pander) # nice tables

df <- read_dta("simulated_multilevel_data.dta") # read in data

pander(head(df)) # nice table

```

```{r}
#| echo: false
#| output: false

# KEEP THIS CHUNK FOR INFORMATIONAL PURPOSES!!!

library(JuliaCall)

# OS dependent location of Julia

switch(Sys.info()[['sysname']],
       Windows= {julia_setup(JULIA_HOME = "C:/Users/agrogan/AppData/Local/Programs/Julia-1.10.2/bin/")},
       Darwin = {julia_setup(JULIA_HOME = "/Applications/Julia-1.8.app/Contents/Resources/julia/bin")})

```
