# Multilevel Visualization

> "Persist and verify... The power that we abdicate to others out of our insecurity - to others who insult us with their faux-intuition or their authoritarian smugness - that comes back to hurt us so deeply... But the power we wrest from our own certitude - that saves us." [@Cash2017]

## Introduction

Below, I describe the use of [Stata](https://www.stata.com/) [@StataCorp2021:3], [R](https://www.r-project.org/)[^ggplot2] [@RProgram; @Wickham2016], and [Julia](https://www.julialang.org/) [@JuliaArticle] to visualize multilevel models. 

::: {.callout-tip}
## Comparison of Software

See my discussion of the advantages and disadvantages of different software in the Appendix on estimation of multilevel models with different software.
:::

[^ggplot2]: In R, I use the `ggplot2` [@Wickham2016] library.

## The Data {#sec-data}

The examples use the `simulated_multilevel_data.dta` file from [*Multilevel Thinking*](https://agrogan1.github.io/multilevel-thinking/simulated-multi-country-data.html). Here is a [direct link](https://github.com/agrogan1/multilevel-multilingual/raw/main/simulated_multilevel_data.dta) to download the data.

```{r}
#| echo: false
#| output: false

file.copy("../multilevel-thinking/simulate-and-analyze-multilevel-data/simulated_multilevel_data.dta", 
          ".",
          overwrite = TRUE) # copy over most recent version

file.copy("../multilevel-thinking/simulate-and-analyze-multilevel-data/simulated_multilevel_longitudinal_data.dta", 
          ".",
          overwrite = TRUE) # copy over most recent version

```

```{r}
#| echo: false
#| label: tbl-multilingual1
#| tbl-cap: Sample of Simulated Multilevel Data

library(haven) # read Stata

library(pander) # nice tables

df <- read_dta("simulated_multilevel_data.dta") # read in data

pander(head(df)) # nice table

```

```{r}
#| echo: false
#| output: false

# KEEP THIS CHUNK FOR INFORMATIONAL PURPOSES!!!

library(JuliaCall)

# OS dependent location of Julia

switch(Sys.info()[['sysname']],
       Windows= {julia_setup(JULIA_HOME = "C:/Users/agrogan/AppData/Local/Programs/Julia-1.10.2/bin/")},
       Darwin = {julia_setup(JULIA_HOME = "/Applications/Julia-1.8.app/Contents/Resources/julia/bin")})

```
